Analysis after review

### 2020-04-28 reports/DRM_exp/analysis_DRM_after_review.Rmd
add context entropy analysis

>>>>

## Context entropy

```{r}
cont_entropy <- read_csv(here("data/exp_DRM1/cats_entrophy.csv"), col_names = F) %>% rename(category = X1, cont_entropy = X2) %>% mutate(category = str_replace(category, "_", " "))
df_cont_entropy <- df %>% left_join(cont_entropy, by = "category") 
df_cont_entropy %>% 
  ggplot(aes(x = category, y = correct, col = type, group = type)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  stat_summary(fun.y = "mean", geom = "line") + 
  scale_x_discrete(guide = guide_axis(n.dodge=3))
